


\title{Exponential Expressions and Functions}

\maketitle
\large{
\noindent 
Dear Teachers and Students,\\

\noindent
This booklet offers problems on systems of equations with two and three variables. The "solutions" and video packages include graphing, substitution, elimination, and matrix methods such as Cramer's Rule and row operations, just to name a couple. To maximize your learning, try solving the problems before reviewing the solutions. This approach will enhance your aptitude in the subject matter and better prepare you for both in-class and standardized tests.\\

\noindent
Additionally, a video solutions package is available, featuring 10 solved problems that are representative of the problem set in this booklet. In these videos, we thoroughly work through each problem and explain my approach to finding the solution.\\
\noindent


Please note that this worksheet is designed for practice and reinforcement, not as an initial lesson on the material. We assume that you are already familiar with these concepts from lectures and classes. The purpose of these problems is to help you solidify your understanding and master the material through varied difficulty levels.\\

\noindent
Thank you for supporting our work. We hope that you find this resource valuable. Please share your feedback and suggestions with us using the form provided on our page.\\


\noindent
Sincerely,\\
B2B STEM Team


\newpage

% Copyright and Usage Restrictions
\begin{center}
\fbox{\begin{minipage}{0.9\textwidth}
\centering
\textbf{\large COPYRIGHT AND USAGE NOTICE}
\vspace{0.3cm}

\textcolor{blue}{\textbf{Personal Use License}}
\vspace{0.2cm}

\textbf{Copyright Notice:} This educational material is protected by copyright law. All rights reserved.
\vspace{0.1cm}

\textbf{What You Can Do (Personal Use):}
\begin{itemize}
\item Use this material for your own personal study and practice
\item Print copies for your personal use only
\item Make handwritten notes and annotations on your copies
\item Store digital copies on your personal devices for your own use
\end{itemize}

\textbf{Usage Limitations:}
\begin{itemize}
\item This license is for personal use by the purchaser only
\item Please do not share, distribute, or copy this material for others
\item Commercial use (including classroom teaching, tutoring, or institutional use) requires a separate license
\item Please do not post online, email to others, or upload to shared platforms
\item Each person who wants to use this material should purchase their own copy
\end{itemize}

\vspace{0.1cm}
\textit{For teachers, tutors, and educational institutions: Please contact us about our educational licensing options.}
\vspace{0.1cm}

\textbf{We appreciate your understanding and respect for our work. By using this material, you agree to these reasonable terms.}
\end{minipage}}
\end{center}


.\par
\setlength{\columnsep}{2.5cm} % Set the gap between columns
%\setlength{\columnseprule}{0.5pt} % Add a thin vertical rule


\graphicspath{{exponentials/images}}
\input{exponentials/properties}
\input{exponentials/problems}
\input{exponentials/answers}
\input{exponentials/solutions}

